MSAD_PCA_Walkthrough

### 2017-12-29 README.Rmd
update
Updated package site to new CRAN and Travis badges, including number of downloads badge.

[![Travis-CI Build Status](https://travis-ci.com/gabrielodom/mvMonitoring.svg?token=ZzKTz9X2qQxWeqCPkaKq&branch=master)](https://travis-ci.com/gabrielodom/mvMonitoring)

>>>>

[![Travis-CI Build Status](https://travis-ci.org/gabrielodom/mvMonitoring.svg?branch=master)](https://travis-ci.org/gabrielodom/mvMonitoring)
[![CRAN Downloads](https://cranlogs.r-pkg.org/badges/grand-total/mvMonitoring)](https://cranlogs.r-pkg.org/badges/grand-total/mvMonitoring)
![CRAN Build Status](http://www.r-pkg.org/badges/version/mvMonitoring)
